Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Jupiter-Sized Planet in IC~2602

### 2020-06-23 paper/ms.tex
update manuscript

\documentclass[12pt,twocolumn,tighten]{aastex62}
%\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex62}
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage[caption=false]{subfig} % for subfloat
\usepackage{enumitem} % for specific spacing of enumerate
\usepackage{epigraph}

@@

\input{authors.tex}

% TODO: SpType subtype?
\begin{abstract}
  We report the discovery of TOI 837.01 and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA {\it Transiting Exoplanet Survey Satellite} (TESS), the ESA
  Gaia mission, ground-based photometry, and spectroscopy from
  CTIO1.5/CHIRON, MPG2.2/FEROS, and AAT/Veloce.  We find that
  TOI$\,$837 is a $T=9.9$ G-dwarf in IC~2602 (the ``Southern
  Pleiades'').  The star and validated planet are therefore 30$\pm$20
  million years old.  The planet is warm ($P = 8.32\,{\rm d}$) and
  roughly Jupiter-sized.  However, its transits are grazing: $b >
  0.92$ at 3$\sigma$.  From TESS photometry alone, the planetary size
  lies within 0.58--3.87 $R_{\rm Jup}$, due to the degeneracy between
  the planetary size and the impact parameter of the transit.  From
  radial velocity monitoring, we limit the mass of planet to less than
  2.XX $M_{\rm Jup}$ (3$\sigma$).  Grazing transits are cause for
  concern: they usually are indicative of astrophysical false
  positive scenarios.  Our follow-up data show that such scenarios are
  highly unlikely.  Multi-color photometry requires eclipsing
  companions to have nearly identical color as TOI$\,$837, ruling out
  hierarchical eclipsing binary scenarios.  Background eclipsing
  binary scenarios are limited by speckle imaging, but formally remain
  a 0.2\% possibility.  TOI 837.01 is therefore a validated adolescent
  exoplanet.  Further observations of its stellar obliquity,
  atmosphere, and mass should confirm its planetary nature beyond
  doubt, and could improve our understanding of how the physical and
  orbital properties of exoplanets change in time.
\end{abstract}

@@

\begin{figure*}[t!]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf TESS light curve of \tn\ from Sectors 10 and 11.} {\it Top}:
    \texttt{PDCSAP} median-subtracted relative flux at 2-minute
    sampling in units of parts-per-thousand ($\times 10^{-3}$).
    Spot-induced stellar variability is the dominant signal.  Dashed
    lines show the five transits observed by TESS.  {\it Bottom}:
    Zoomed windows of individual transits.  Red points are manually
    identified stellar flares.
		\label{fig:rawzoom}
	}
\end{figure*}

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.7\textwidth]{f2a.pdf}
		}

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.7\textwidth]{f2b.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{
    {\bf Joint TESS and multicolor photometry.} {\it Top:}
    Phase-folded TESS transit. Gray points are 2-minute PDCSAP flux
    measurements, detrended with a 0.3-day robust Huber spline (see
    Section~\ref{subsec:tess}).  Black points are binned to 6 minute
    intervals.  The line shows the transit model corresponding to the
    median transit parameters (Table~2).  {\it Bottom:} Multicolor
    photometry from the El Sauce 0.36m.  The consistent transit depths
    between TESS-band and the bluer Cousins-R and Johnson-B bandpasses
    rules out select false positive scenarios.
    \label{fig:jointphot}
	}
\end{figure*}

@@

Figure~\ref{fig:rawzoom} shows the data.  The dominant modulation
induced by starspots coming into and out of view has a peak-to-peak
amplitude of about 2.3\%, and a period of about 3 days.  The dips
suggestive of a grazing transiting planet recur roughly every 8 days,
and have a depth of about 0.4\%.  A few flares are visible.  A
phase-folded version of the TESS transits with starspot variability
removed is shown in Figure~\ref{fig:jointphot}, and is described in
depth in Section~\ref{subsec:planet}.

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Scene used for blend analysis.}
    {\it Top:} Mean TESS image of \tn\ over Sector~10, with a
    logarithmic grayscale. The yellow star is the position of \tn.
    Orange circles are neighboring stars with $T<16$, scaled such that
    brighter stars are larger. The \texttt{X} and \texttt{/} hatches
    show the apertures used to measure the background and target star
    flux, respectively. Dashed lines of constant declination and right
    ascension are shown.  {\it Bottom:} Digitized Sky Survey $R$-band
    image of the same field, with a linear grayscale. The circles show
    apertures of radii 1, 1.5, and 2.25 pixels used in our blend
    analysis (Section~\ref{subsec:validation}).  Two stars of interest
    are ``Star A'' and ``Star B'', which were eventually excluded as
    being possible sources of the transits.
		\label{fig:scene}
	}
\end{figure}

@@

The Gaia imaging, as represented by its point-source catalog, provides
the initial context for analyzing the TESS data.  Stars brighter than
$T=16$, as queried from the Gaia DR2 source catalog, are shown with
orange circles in Figure~\ref{fig:scene}, overlaid on the DSS2 plates
and TESS image.  Given its galactic latitude of $b=-6^\circ$, it is
not surprising that the field of \tn\ is crowded.  The stars that were
of immediate concern for our false positive analysis were as follows.
\begin{itemize}
  \item \tn\ $\equiv$ TIC 460205581 ($T=9.9$). The target star.
  \item Star A $\equiv$ TIC 847769574 ($T=14.6$), $2.3$'' west. The
    proper motions and parallax of this star imply it is comoving with
    \tn, though with a physical separation of $6.6\pm 0.1\,{\rm pc}$,
    it may not be bound.
  \item Star B $\equiv$ TIC 460205587 ($T=13.1$), $5.4$'' north.  The
    Gaia parallax implies this is a giant background star.
\end{itemize}
An additional source, TIC 847769581, is $4.9$'' from the target, but
too faint (T=18.8) to be the source of the observed transit signal.

The Gaia DR2 data for Star A seems poorly behaved.  While
Star A has $G=15.1$, and $Bp=14.9$, no $Rp$ magnitude is reported.
Correspondingly, no RUWE\footnote{ See the Gaia
DPAC technical note GAIA-C3-TN-LU-LL-124-01,
\url{http://www.rssd.esa.int/doc_fetch.php?id=3757412}, accessed
2020-06-22. } value is available.  The astrometric
reduced $\chi^2$ ($\chi^2 / (N-5)$, for $N$ the number of good
astrometric observations) seems rather poor, at $8.6$.  We suspect
that the photometric failure to produce an $Rp$ magnitude, as well as
the poor astrometric fit, are likely due to blending with \tn.

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ 
    {\bf SOAR HRCam contrast limits derived from point-source
    injection-recovery experiments.} Star A ($\Delta T=4.7$,
    $\rho=2.3$'' west) is detected in the autocorrelation function, in
    addition to being a resolved Gaia source.  It is co-moving with
    \tn, and its parallax and on-sky position imply that it is
    physically separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.
		\label{fig:soar}
	}
\end{figure}

@@

We observed four transits with the 0.36m at Observatario El Sauce,
located in the R\'io Hurtado Valley in Chile, and operated by
co-author P{.}~Evans.  The observations were obtained in Cousins-R
band on the nights of 1 April 2020 and 26 April 2020, Cousins-I band
on the night of 21 May 2020, and Johnson-B band on the night of 14
June 2020.  The final 14 June transit began shortly after twilight.

@@

{\bf LGB TODO: Describe custom analysis of apertures}

@@

\begin{figure}[t!]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{f3.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Radial velocities.}
		\label{fig:rvs}
	}
\end{figure}

@@

\subsubsection{CHIRON}
We acquired nine spectra with CTIO1.5/CHIRON, from January 28 2020 through
March 14 2020.
Six met our signal-to-noise requirements for radial velocity
measurements.

{\bf George TODO: please describe the formal secondary line search in
more depth in this paragraph}
We searched for secondary lines in the CHIRON spectra by
cross-correlating against a {\bf template of some kind}.
This rules out lines with flux ratios of $\approx 2\%$, if the
lines are well-separated in velocity.
We measured the radial velocities against the same template.
To derved the star's physical parameters, we cross-correlated the
template against {\bf something}, and used the {\bf
\texttt{nameofcode}}. 
This yielded:
\begin{align}
  T_{\rm eff}   &= 5946 \pm 39\,{\rm K}, \nonumber \\
  \log g        &= 4.48 \pm 0.03, \nonumber \\
  {\rm [Fe/H] } &= -0.065 \pm 0.035, \nonumber \\
  v \sin i      &= 17.48 \pm 0.15\,{\rm km\,s}^{-1}.
\end{align}
These spectroscopic parameters were used in our final analysis 
of the system (Section~\ref{sec:system}).

\subsubsection{FEROS}
We acquired N spectra with XXX/FEROS.

\subsubsection{Veloce}
We acquired M spectra with AAT/Veloce.

@@

\begin{figure*}[t!]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Astrophysical false positive scenarios.}
		{\it Top}: for bound companions,
		{\it Bottom}: for unassociated companions along the same line of
		sight.
		\label{fig:fpscenario}
	}
\end{figure*}

"""Validation is the process of statistically arguing that a
transit-like signal is due to a planet rather than an astrophysical
false positive. """
(CITE blender, Torres+04,05,10; vespa Morton 12, 15; pastis Diaz+14
Santerne+15; triceratops Giacalone \& Dressing 20).

Many validation analyses are inherently flawed because they do
not deal with the fact that you are conditioned on having observed
many stars, and having found an eclipsing system.

Figure~\ref{fig:fpscenario} provides a visual summary of the possible
astrophysical false positive scenarios.  If the \tn\ signal is not
planetary, it must come from the near-total eclipse of a background
star (a BEB), or else a hierarchical companion of the primary star
(an HEB).  It must also be verified that to the angular resolution
possible, the transit signal originates from \tn, and not a
neighboring star (an NEB).
We proceed by describing each constraint in detail.

\subsection{Limits on Companions from the Transit Depth}

In HEB and BEB scenarios, the flux from \tn\ and the true eclipsing
binary host would blend together, reducing the ``true'' eclipse depth
$\delta_{\rm true}$ to produce the observed depth
$\delta_{\rm obs}$:
\begin{equation}
  \delta_{\rm obs}
  = 
  \delta_{\rm true} \frac{F_{\rm neighbor}}{F_{\rm total}},
\end{equation}
where the total flux and the flux from the neighbor are labelled as
such.  The requirement that the eclipse is produced by stars and that
$\delta_{\rm true} < 0.5$ translates to a bound on the faintest
possible blended companion stars:
\begin{equation}
    \Delta m < - \frac{5}{2} \log_{10} \left( \frac{0.5}{\delta_{\rm obs}} \right).
\end{equation}
For \tn\ ($T=9.93$), this implies that any stellar companion invoked
to explain the transit depth must be brighter than $T=15.07$.

Typically, the shape of the transits enables this argument to be scaled to even
more restrictive depths (e.g., CITE Seager 2003, Vanderburg+2019,
Rizzuto+2020, David+2018 1298Tau).  However, since the transits of
\tn\ are grazing, these arguments do not apply.

\subsection{Limits on Companions from Imaging}

\subsubsection{Gaia Imaging}
{\it empty}

\subsubsection{Speckle Imaging}

We convert the contrast ratios obtained through the SOAR imaging to
constraints on the masses of putative companions following Montet+2014
(CITE and others!).  We employed the Baraffe+2003 models for
substellar mass objects and the MESA isochrones for stellar mass
objects (Choi et al XXXX).  We assumed that the system age was 35 Myr,
to ensure that companions would be at a plausible state of
contraction.

Due to the specific filters of the SOAR HRcam imager, we further
assumed that all sources had blackbody spectra. While this is clearly
false, we do not readily have access to the planetary and stellar
atmosphere models needed for the correct calculation. However, the
Baraffe+2003 and MESA models do report effective temperatures and
bolometric luminosities.  We opt to use these theoretical quantities,
combined with the measured transmission functions, to calculate the
absolute magnitudes in the HRCam bandpasses (CITE Tokovinin 2018
summary paper with the bandpasses).

\subsubsection{Patient Imaging}
    Archival SERC-J and AAO-SES plates are available for the \tn\
field\footnote{\url{https://archive.stsci.edu/cgi-bin/dss_form}}.
These plates were acquired in 1982 and 1992, respectively.
For high proper motion stars archival imagery can be used to
detect slowly moving background stars that might be an
astrophysical false-positive source
({\it e.g.}, \citealt{huang_pimen_2018}, CITE VANDERBURG 19).
However \tn\ has only moved $\approx0.7''$ between 1982 and
present, in comparison to the $\approx2.0''$ FWHM of the target on
the plates.
We therefore cannot resolve it with great confidence from
background sources not already resolved through more modern
imaging.

\subsection{Limits on Companions from Radial Velocities}

The combined radial velocities from FEROS, CHIRON, and Veloce 
can be used to place limits on the presence of massive, close-in
bounds companion to \tn.

We derived the relevant limits using \texttt{radvel} \citep{fulton_radvel_2018}.
We assumed circular orbits for the massive companion.
We then fitted the RV data for the semiamplitude, period, time
of conjunction,
instrument offsets, and jitter parameters.
We placed a wide log-uniform prior on the semiamplitude
and period to ensure appropriate sampling of the relevant
spaces.
($\log K \sim \mathcal{U}(1,10^5)$, $\log P \sim \mathcal{U}(0.1, 10^{15})$).

We then converting the resulting posterior in period and semiamplitude
to minimum mass and semi-major axis assuming Kepler's third law.
The resulting $3\sigma$ limits are shown in Figure~\ref{fig:fpscenario}.

\subsection{Limits on Companions from Time-Series Photometry}

\subsubsection{TESS}
We examined the CDIPS FFI light curves of the target, which are
available on MAST \citep{bouma_cluster_2019}. Three light curves are
available, based on photometric apertures with a radius of 1, 1.5, or
2.5 pixels.  In the raw difference-image light-curves, as well as the
PCA-detrended light-curves, dips of depth $\approx$0.35\% are visible,
and their properties do not significantly vary with aperture size.
Within $\approx20$'', the dips are consistent with originating from
the target star.

\subsubsection{Custom Apertures on Ground-Based Time-Series Photometry}
% See "TOI-837 : a planet!" thread, May 2020

\subsubsection{Color Photometry}

@@

For a lower limit on $\delta_{\rm R_C}$ of 32 parts per thousand,
we found that the transition between systems that would produce
eclipses that no matter what were ``too red'', and systems that would
produce eclipses that could be sufficiently blue happens in \tn\ (for
${\rm R_C}$-band) at 0.54$M_\odot$.
The corresponding limit is shown in Figure~\ref{fig:fpscenario}.

{\bf If we could obtain a similar limit in B-band, it would 
	solidify this result (because it would drive the HEB system to be even bluer).}

@@

\newpage
\subsubsection{Summary}

>>>>

\documentclass[12pt,twocolumn,tighten]{aastex63}
%\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex63}
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage[caption=false]{subfig} % for subfloat
\usepackage{enumitem} % for specific spacing of enumerate
\usepackage{epigraph}

@@

\suppressAffiliations
%\NewPageAfterKeywords
\input{authors.tex}

% TODO: SpType subtype?
\begin{abstract}
  We report the discovery of TOI 837.01 and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA TESS mission, the ESA Gaia mission, ground-based photometry,
  and spectroscopy from CHIRON, FEROS, and Veloce.  We find that
  TOI$\,$837 is a $T=9.9$ G0 dwarf in IC 2602 (the ``Southern
  Pleiades'').  The star and validated planet are therefore 30$\pm$15
  million years old.  The planet is warm ($P = 8.32\,{\rm d}$) and
  roughly Jupiter-sized.  However, its transits are grazing: $b >
  0.92$ at 3$\sigma$.  From TESS photometry alone, the planetary size
  lies within 0.58--3.87 $R_{\rm Jup}$, due to the degeneracy between
  the planetary size and the impact parameter of the transit.  From
  radial velocity monitoring, we limit the mass of planet to less than
  2.XX $M_{\rm Jup}$ (3$\sigma$).  Grazing transits are cause for
  concern: they usually are indicative of astrophysical false positive
  scenarios.  Our follow-up data show that such scenarios are highly
  unlikely.  Multi-color photometry requires eclipsing companions to
  have nearly identical color as TOI$\,$837, ruling out hierarchical
  eclipsing binary scenarios.  Background eclipsing binary scenarios
  are limited by speckle imaging, but formally remain a 0.2\%
  possibility.  TOI 837.01 is therefore a validated adolescent
  exoplanet.  Further observations of its stellar obliquity,
  atmosphere, and mass should confirm its planetary nature beyond
  doubt, and could improve our understanding of how the physical and
  orbital properties of exoplanets change in time.
\end{abstract}

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf TESS light curve of \tn\ from Sectors 10 and 11.} {\it Top}:
    \texttt{PDCSAP} median-subtracted relative flux at 2-minute
    sampling in units of parts-per-thousand ($\times 10^{-3}$).
    Spot-induced stellar variability is the dominant signal.  Dashed
    lines show the five transits observed by TESS.  {\it Bottom}:
    Zoomed windows of individual transits.  Red points are manually
    identified stellar flares.
		\label{fig:rawzoom}
	}
\end{figure*}

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f2a.pdf}
		}

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f2b.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{
    {\bf Joint TESS and multicolor photometry.} {\it Top:}
    Phase-folded TESS transit. Gray points are 2-minute PDCSAP flux
    measurements, detrended with a 0.3-day robust Huber spline (see
    Section~\ref{subsec:tess}).  Black points are binned to 6 minute
    intervals.  The line shows the transit model corresponding to the
    median transit parameters (Table~2).  {\it Bottom:} Multicolor
    photometry from the El Sauce 0.36m.  The consistent transit depths
    between TESS-band and the bluer Cousins-R and Johnson-B bandpasses
    rules out select false positive scenarios.
    \label{fig:jointphot}
	}
\end{figure*}

@@

Figure~\ref{fig:rawzoom} shows the data.  The dominant modulation
induced by starspots coming into and out of view has a peak-to-peak
amplitude of about 2.3\%, and a period of about 3 days.  The dips
suggestive of a grazing transiting planet recur roughly every 8 days,
and have a depth of about 0.4\%.  A few flares are visible.  A
phase-folded view of the TESS transits with starspot variability
removed is shown in Figure~\ref{fig:jointphot}, and is described in
depth in Section~\ref{subsec:planet}.

%TODO: you must check custom lightkurve apertures, too

%FIXME: this paragraph doesn't really belong here?
We examined the CDIPS FFI light curves of the target, which are
available on MAST \citep{bouma_cluster_2019}. Three light curves are
available, based on photometric apertures with a radius of 1, 1.5, or
2.5 pixels.  In the raw difference-image light-curves, as well as the
PCA-detrended light-curves, dips of depth $\approx$0.35\% are visible,
and their properties do not significantly vary with aperture size.
Within $\approx20$'', the dips are consistent with originating from
the target star.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Scene used for blend analysis.}
    {\it Top:} Mean TESS image of \tn\ over Sector~10, with a
    logarithmic grayscale. The yellow star is the position of \tn.
    Orange circles are neighboring stars with $T<16$, scaled such that
    brighter stars are larger. The \texttt{X} and \texttt{/} hatches
    show the apertures used to measure the background and target star
    flux, respectively. Dashed lines of constant declination and right
    ascension are shown.  {\it Bottom:} Digitized Sky Survey $R$-band
    image of the same field, with a linear grayscale. The circles show
    apertures of radii 1, 1.5, and 2.25 pixels used in our blend
    analysis (Section~\ref{subsec:validation}).  Two stars of interest
    are ``Star A'' and ``Star B'', which were eventually excluded as
    being possible sources of the transits.
		\label{fig:scene}
	}
\end{figure}

@@

The Gaia imaging, reduced to its point-source catalog, provides
the initial context for analyzing the TESS data.  Stars brighter than
$T=16$, as queried from the Gaia DR2 source catalog, are shown with
orange circles in Figure~\ref{fig:scene}, overlaid on the DSS2 plates
and TESS image.  Given its galactic latitude of $b=-6^\circ$, it is
not surprising that the field of \tn\ is crowded.  The resolved stars
that were of immediate concern for our false positive analysis were as
follows.
\begin{itemize}
  \item \tn\ $\equiv$ TIC 460205581 ($T=9.9$). The target star.
  \item Star A $\equiv$ TIC 847769574 ($T=14.6$), $2.3$'' west. The
    proper motions and parallax of this star imply it is comoving with
    \tn, though with a physical separation of $6.6\pm 0.1\,{\rm pc}$,
    it may not be bound.
  \item Star B $\equiv$ TIC 460205587 ($T=13.1$), $5.4$'' north.  The
    Gaia parallax implies this is a giant background star.
\end{itemize}
An additional source, TIC 847769581, is $4.9$'' from the target, but
too faint ($T=18.8$) to be the source of the observed transit signal.

The Gaia DR2 data for Star A seems poorly behaved.  While Star A has
$G=15.1$, and $Bp=14.9$, no $Rp$ magnitude is reported.
Correspondingly, no RUWE\footnote{ See the Gaia DPAC technical note
GAIA-C3-TN-LU-LL-124-01,
\url{http://www.rssd.esa.int/doc_fetch.php?id=3757412}, accessed
2020-06-22. } value is available.
% The astrometric reduced $\chi^2$ ($\chi^2 / (N-5)$, for $N$ the number
% of good astrometric observations) seems rather poor, at $8.6$.
We suspect that the photometric failure to produce an $Rp$ magnitude,
as well as its poor astrometric fit, are likely due to blending with
\tn.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ 
    {\bf SOAR HRCam contrast limits derived from point-source
    injection-recovery experiments.} Star A ($\Delta T=4.7$,
    $\rho=2.3$'' west) is detected in the autocorrelation function, in
    addition to being a resolved Gaia source.  It is co-moving with
    \tn, and its parallax and on-sky position imply that it is
    physically separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.
		\label{fig:soar}
	}
\end{figure}

@@

\paragraph{Acquisition}
We observed four transits with the 0.36m at Observatario El Sauce,
located in the R\'io Hurtado Valley in Chile, and operated by
co-author P{.}~Evans.  The observations were obtained in Cousins-R
band on the nights of 1 April 2020 and 26 April 2020, Cousins-I band
on the night of 21 May 2020, and Johnson-B band on the night of 14
June 2020.  The final 14 June transit began shortly after twilight.

@@

%TODO TODO
% See "TOI-837 : a planet!" thread, May 2020
\paragraph{Custom aperture analysis}
{\bf LGB TODO: Describe custom analysis of apertures. }
"""
While ``Star A'' was detected in the SOAR images, our ground-based
photometry rules it out as a possible source of the eclipse signal
(Section~\ref{subsec:groundphot}).
"""

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{f3.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Radial velocities.}
		\label{fig:rvs}
	}
\end{figure}

@@

\subsubsection{SMARTS 1.5m / CHIRON}
\label{subsec:chiron}

We acquired nine spectra using CHIRON at the SMARTS 1.5m telescope at
Cerro Tollo Inter-American Observatory, Chile
\citep{tokovinin_chironfiber_2013}.  Six met our signal-to-noise
requirements for radial velocity measurements and stellar parameter
extraction.  We used CHIRON in its image slicer configuration,
yielding a spectral resolution of $\approx 79{,}000$ across
415--880$\,$nm.

{\bf George TODO: please describe the formal secondary line search in
more depth in this paragraph} We searched for secondary lines in the
CHIRON spectra by cross-correlating against a {\bf template of some
kind}.  This rules out lines with flux ratios of $\approx 2\%$, if the
lines are well-separated in velocity.  To derive the star's physical
parameters, we cross-correlated the template against {\bf something},
and used the {\bf \texttt{nameofcode}}.  This yielded:
\begin{align}
  T_{\rm eff}   &= 5946 \pm 39\,{\rm K}, \nonumber \\
  \log g        &= 4.48 \pm 0.03, \nonumber \\
  {\rm [Fe/H] } &= -0.065 \pm 0.035, \nonumber \\
  v \sin i      &= 17.48 \pm 0.15\,{\rm km\,s}^{-1}.
\end{align}
These spectroscopic parameters were used in our final analysis of the
system (Section~\ref{sec:system}).  We measured the radial velocities
through a least-squares deconvolution of the observed spectra against
the same synthetic template.  The resulting velocities are given in
Table~\ref{tab:rvs}, and shown in Figure~\ref{fig:rvs}.

\subsubsection{FEROS}
We acquired 13 spectra using the FEROS echelle spectrograph, mounted
on the MPG 2.2m telescope at the European Soutern Observatory in La
Sille, Chile \citep{kaufer_commissioning_1999}.  FEROS has a
resolution of $\approx 48{,}000$ across a spectra range of
350--920$\,$nm. It has a remarkably high efficiency of $\approx 20\%$.

We used the dedicated instrument pipeline to extract 1-dimensional,
wavelength calibrated spectra.  To measure radial velocities, {\bf
Rafael TODO: what procedure was used?  What software packages?}.  The
velocities are given in Table~\ref{tab:rvs}, and shown in
Figure~\ref{fig:rvs}.

\subsubsection{Veloce}
We acquired 34 spectra over 10 visits of \tn\ with using the Veloce
spectrograph, mounted on the AAT 4.0m telescope at Siding Spring
Observatory near Coonabarabran, Australia \citep{gilbert_veloce_2018}.
In Rosso form, Veloce provides coverage from 600--950$\,$nm at a
spectral resolution of $\approx 80{,}000$.

Many of the exposures were taken in average or poor seeing conditions,
when fiber-to-fiber cross-contamination on the IFU-style fiber feed is
strongest.  To reduce the spectra to velocities, we cross-correlated
against a high S/N template of $\delta$ Pavonis.  The velocity RMS
seen across each visit was hundreds of meters per second, likely due to
uncorrected fiber-to-fiber cross-contamination.  For
analysis purposes, we averaged across each visit, and set the velocity
uncertainties as the standard deviation in the per-visit exposures.
The velocities are given in Table~\ref{tab:rvs}, and shown in
Figure~\ref{fig:rvs}.

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Astrophysical false positive scenarios.}
		{\it Top}: for bound companions,
		{\it Bottom}: for unassociated companions along the same line of
		sight.
		\label{fig:fpscenario}
	}
\end{figure*}

``Validating'' a transiting planet means statistically arguing that
the data are much more likely to be caused by a planet than by other
astrophysical false positives.  The concept of validation has been
developed and calibrated by {\it e.g.},
\citet{torres_modeling_2011,morton_efficient_2012,diaz_pastis_2014,santerne_pastis_2015,morton_false_2016}
and \citet{giacalone_triceratops_2020}.  ``Validation'' is different
from ``confirmation'', which means that there is overwhelming evidence
that the data must be explained by a planet, for instance through
combined transits and a mass measurement.

Assuming the eclipse has been localized to the target star within the
available angular resolution, potential false positive scenarios
include eclipses of a background binary (BEB), eclipses of a
hierarchical companion to the primary star (HEB), and the possibility
that the eclipses of \tn\ are simply caused by a stellar companion,
rather than a planetary one (EB).

Figure~\ref{fig:fpscenario} provides a visual summary of the possible
astrophysical false positive scenarios, as well as our ability to rule
them out based on our combined photometry, velocimetry, and imaging.
We proceed by describing each constraint in detail, and then present a
statistical calculation using \texttt{VESPA}
\citep{morton_efficient_2012} to demonstrate that the probability \tn\
is an astrophysical false positive is small enough to consider it
``validated''.

\subsection{Constraints on False Positive Scenarios}

\subsubsection{Transit Depth}
In HEB and BEB scenarios, the flux from \tn\ and the true eclipsing
binary host would blend together, reducing the ``true'' eclipse depth
$\delta_{\rm true}$ to produce the observed depth
$\delta_{\rm obs}$:
\begin{equation}
  \delta_{\rm obs}
  = 
  \delta_{\rm true} \frac{F_{\rm neighbor}}{F_{\rm total}},
\end{equation}
where the total flux and the flux from the neighbor are labelled as
such.  The requirement that the eclipse is produced by stars and that
$\delta_{\rm true} < 0.5$ translates to a bound on the faintest
possible blended companion stars:
\begin{equation}
  \Delta m < -\frac{5}{2} \log_{10} \left( \frac{0.5}{\delta_{\rm obs}} \right).
\end{equation}
For \tn\ ($T=9.93$), this implies that any stellar companion invoked
to explain the transit depth must be brighter than $T=15.07$.  In
Figure~\ref{fig:fpscenario}, we set the spatial limit to 2$''$ based
on the precision at which we have localized the transits using
seeing-limited ground-based photometry.

Typically, the shape of the transits enables this argument to be
scaled to even more restrictive depths \citep[{\it
e.g.},][]{seager_unique_2003,vanderburg_hr858_2019,rizzuto_tess_2020}
However, since the transits of \tn\ are grazing, the second and third
contact points do not occur, and the shape of the transit is not
restrictive.

\subsubsection{Speckle Imaging}
The contrast limits obtained through the SOAR $I$-band speckle imaging
(Section~\ref{subsec:speckle}) are shown in
Figure~\ref{fig:fpscenario}.  While ``Star A'' was detected in the
SOAR images, our ground-based photometry rules it out as a possible
source of the eclipse signal (Section~\ref{subsec:groundphot}).  To
convert the remaining contrast constraints to limits on the masses of
putative bound companions, we opted to employ the
\citet{baraffe_evolutionary_2003} models for substellar mass objects
and the MIST isochrones for stellar mass objects
\citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015,dotter_mesa_2016,choi_mesa_2016}.
We assumed that the system age was 35 Myr, to ensure that companions
would be at a plausible state of contraction.

To convert from theoretical effective temperatures and bolometric
luminosities to expected magnitudes in instrumental bandpasses, we
assumed that all soruces had blackbody spectra.  While this is clearly
a simplification, the custom instrumental bandpasses prevented a fully
consistent stellar evolutionary calculation.  Using the theoretical
stellar parameters and the measured transmission functions
\citep{tokovinin_ten_2018}, we then calculated the apparent magnitude
of putative stellar companions of different masses, and interpolated
to produce the scale shown on the right in
Figure~\ref{fig:fpscenario}.

\subsubsection{Not SB2}
As described in Section~\ref{subsec:chiron}, we searched the CCFs of
the CHIRON spectra to determine whether \tn\ is double-lined.  For a
stellar companion well-separated in velocity, this typically shows
companions with flux-fractions $F_2/F_1 \gtrsim 2\%$.  For plotting
purposes, in Figure~\ref{fig:fpscenario} we have assumed a
flux-fraction limit of 5\% ($\Delta {\rm mag} \approx 3.25$).

\subsubsection{RVs}
The combined radial velocities from FEROS, CHIRON, and Veloce can be
used to place limits on the presence of massive, close-in bounds
companion to \tn.  We derived the relevant limits using
\texttt{radvel} \citep{fulton_radvel_2018}.  We assumed circular
orbits for the massive companion.  We then fitted the RV data for the
semiamplitude, period, time of conjunction, instrument offsets, and
jitter parameters.  We placed a wide log-uniform prior on the
semiamplitude and period to ensure appropriate sampling of the
relevant spaces.  ($\log K \sim \mathcal{U}(1,10^5)$, $\log P \sim
\mathcal{U}(0.1, 10^{15})$).  We converted the resulting posterior in
period and semiamplitude to minimum mass and semi-major axis assuming
Kepler's third law.  The resulting $3\sigma$ limits are shown in
Figure~\ref{fig:fpscenario}.

\subsubsection{Multicolor Photometry}
% TODO: this section is ridiculously long. Abbreviate to 2 paragraphs, 3
% at most.

@@

For a lower limit on $\delta_{\rm R_C}$ of 30$\,$ppt,
we found that the transition between systems that would produce
eclipses that no matter what were ``too red'', and systems that would
produce eclipses that could be sufficiently blue happens in \tn\ (for
${\rm R_C}$-band) at 0.38$M_\odot$.
The corresponding limit is shown in Figure~\ref{fig:fpscenario}.
For a $\delta_{\rm B_J}$ limit of 30$\,$ppt, the corresponding mass
limit is 0.82$M_\odot$.

@@

\subsubsection{Gaia}

The ``Gaia'' curve in Figure~\ref{fig:fpscenarios} combines both
point-source detections from imaging, and sources that show an
astrometric excess.  The curve was interpolated from Figure~4 of
\citet{rizzuto_zeitVIII_2018}.  \tn\ has a RUWE statistic of 1.022,
indicative that there are no obviously present astometric companions.
The UWE statistic (square-root of the reduced astrometric $\chi^2$) is
1.38, which is consistent with comparably bright and blue stars
\citep[][Appendix A]{lindegren_gaiasoln_2018}.
